---
title: "myPaintings"
output: github_document
always_allow_html: true
resource_files:
  ./readme
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<link href="readme/adminlte.min.css" rel="stylesheet">
<script src="https://kit.fontawesome.com/3ded47969a.js" crossorigin="anonymous"></script>
<script src="readme/jquery.min.js"></script>
<script src="readme/bootstrap.bundle.min.js"></script>
<script src="readme/adminlte.min.js"></script>

## Overview

This repository contains my contribution to the [Summer 2021 - Shopify Developer Intern Challenge](https://docs.google.com/document/d/1ZKRywXQLZWOqVOHC4JkF3LqdpO3Llpfk_CkZPR8bjak/edit). The task was to build an image repository. 

I decided to build a web application with the framework [Shiny](https://shiny.rstudio.com/) for the R programming language. To prove the capabilities of my application I crawled over 30,000 images of historical paintings from the [Web Gallery of Art](https://www.wga.hu/). Users can collect these paintings and trade them with other users.

## Features

* **User Management**

* **Painting Views**

* **Filter Paintings**

* **Trade Paintings**

## Implementation

### Initialisation

```{r} 
source("./init/source_directory.R")
source_directory("./modules")

set.seed(1)

image_box_ui(
  id = "image",
  image = list(
    owner = "David Barkemeyer",
    painter = "Emanuel Gottlieb Leutze",
    title = "Washington Crossing the Delaware",
    date = "1851",
    location = "Metropolitan Museum of Art, New York",
    type = "historical",
    school = "American",
    url = "https://www.wga.hu/html/l/leutze/delaware.html",
    path = "readme/delaware.jpg",
    is_offered = FALSE
  ),
  type = "browse"
)
```

